Response to the defense feedback

### 2021-06-01 changelog.tex
Updates from Overleaf

The situation is a little different for a machine learning library. In my dissertation, we also evaluated Quincunx on a deep learning model. Each time, we randomly select an item from a dataset (Samples). If the dataset is biased, then we can not get correct results. The good news is that the most well-known data in machine learning is i.i.d. i.i.d. is the foundation of supervised machine learning algorithms. In my dissertation, we used MINIST, a well-known handwriting dataset. We believe the i.i.d. assumption holds under the circumstance.

I have revised my dissertation to include the discussion on iid.

>>>>

The situation is a little different for a machine learning library. In my dissertation, we also evaluated Quincunx on a deep learning model. Each time, we randomly select an item from a dataset (Samples). If the dataset is biased, then we can not get correct results. The good news is that the most well-known data in machine learning is i.i.d. i.i.d. is the foundation of supervised machine learning methods. The assumption of i.i.d. simplify many methods by assuming the data won't change over the time. In my dissertation, we used MINIST, a well-known handwriting digit dataset. We believe the i.i.d. assumption holds under the circumstance.

I have revised my dissertation to include the discussion on i.i.d.
